---
title: "Exploring the BRFSS data"
author: "Javier Montaño"
date: "21 de junio de 2020"
output: html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
```

### Load data



```{r load-data}
load(".\R\Packages\brfss2013.RData")
data1 <- brfss2013 %>% select(cvdinfr4, cvdcrhd4, asthma3, havarth3, sleptim1)
data1$sleptim1 <- gsub("\\b(1|2|3|4|5|6|7)\\b", "Bad Sleepers", data1$sleptim1) #Bad Sleepers
data1$sleptim1 <- gsub("\\b\\d+\\b", "Good Dreamer", data1$sleptim1) #

```



* * *

## Part 1: Data

The data come from a phone survey and specificaly some questions about the sleep time and if the person has some illness, i wanna see the proportion of *Good Sleepers* and *Bad Sleepers* for each illness, for "Good Sleepers" i mean people who spend 8 or more hours asleep

* * *

## Part 2: Research questions

**Research quesion 1: What's the proportion of good and bad dreamers with/without Coronary Heart Disease:**

**Research quesion 2: What's the proportion of good and bad dreamers with/without Asthma:**

**Research quesion 3: What's the proportion of good and bad dreamers with/without Arthritis:**


* * *

## Part 3: Exploratory data analysis


**Research quesion 1: What's the proportion of good and bad dreamers with/without Coronary Heart Disease:**

```{r}
data2 <- data1 %>% filter(cvdcrhd4 != NA)
ggplot(data2) + geom_bar(mapping = aes(x = cvdcrhd4, fill = sleptim1), position = fill) + theme_classic() + scale_fill_brewer(palette = "Accent")

```



**Research quesion 2: What's the proportion of good and bad dreamers with/without Asthma:**

```{r}
data3 <- data1 %>% filter(asthma3 != NA)
ggplot(data3) + geom_bar(mapping = aes(x = asthma3, fill = sleptim1), position = fill) + theme_classic() + scale_fill_brewer(palette = "Accent")

```



**Research quesion 3: What's the proportion of good and bad dreamers with/without Arthritis:**

```{r}
data4 <- data1 %>% filter(havarth3 != NA)
ggplot(data4) + geom_bar(mapping = aes(x = havarth3, fill = sleptim1), position = fill) + theme_classic() + scale_fill_brewer(palette = "Accent")
```
